Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-03-01 paper/main.tex
Adress all comments, main paper

\noindent Generally
\begin{itemize}
    \item Todo's are mostly comments and can be deleted if issue is solved by
        current phrasing
    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
        cite DOI in data availability section
    \item Lescroart is just a small footnote in pPPA vs. aPPA in discussion
        (problem to write more about the paper: it is voxel-wise encoding which
        does not tell a lot about increased vs. decreased activation; "crafted"
        stimuli: 45 min of 850 scenes, made from 33 backgrounds + 2-3 objects
        drawn from pool of 440 objects
    \item maybe "do something with" dice-index
\end{itemize}

@@

\todo[inline]{SE: mit Befund, den Du diskutieren willst beginnen, mit take-home
message enden. COH: bekomme ich nur (und auch nur evtl.) reingepresst, wenn ich
die Discussion komplett umschreibe; take-home message ist aber eh fast überall
drin}

\todo[inline]{SE: es gibt schon andere "event-related" analysen von movies,
oder? COH: habe Paper durchgeguckt: Es gibt wenig bis gar nichts (obwohl
Annotation immer mehr automatisiert werden können); Bzgl. Narrative ist im
Grunde alles "voxel-wise enconding"; Rocca benutzt Annotation, aber auch
"crafted" 23-min Narrative; NeuroScout: bisher absolut (?) keine veröffentlichte
Studie, die NeuroScout genutzt hat; -> Bartels ist Klassiker, steht aber enorm
allein da, und macht aber genau das, was wir machen "Naturalistic Stimulus statt
Traditionell"; insofern: es gibt schon "irgendwie" andere Studien, die etwas mit
Annotation (von Filmen) gemacht haben, die machen aber dann halt auch ganz
anderes Zeug}

%#1 previous studies
Several studies have reported increased hemodynamic activity in the PPA
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects (\citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}).
% auditory semantics unclear
However, reports regarding the correlates of processing spatial information in
verbal stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing of spatial information, we
employed a naturalistic stimuli, a movie and its audio-description, that were
designed for entertainment.

@@

%#11 question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
immanent in both visual and verbal stimuli.

@@

% shortcomings
%#2
Our approach to stimulus annotation and event selection differs from previous
reports in the literature.
% PPA: intro
In an earlier study, \citet{bartels2004mapping} manually annotated the content of
movie frames (color, faces, language, and human bodies) and found that the
functional specialization of brain areas is preserved during movie watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% results
The group results of the movie stimulus' primary contrast yielded a large
cluster that spans the group overlap of individual PPA ROIs from anterior to
posterior.
% confound of higher perception
The cluster extends into more posterior, earlier visual areas could be an
indication that the temporal averaging across events suffered from insufficient
controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames (e.g.,
using the open-source solution ``Pliers''\citep{mcnamara2017developing} for feature extraction from a visual
naturalistic stimulus).

@@

%#12 RSC + LOC
Apart from the PPA, results show significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
activity in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene} for
reviews)
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on
stimulus annotations reveals focussed activation patterns in networks that are
implicated in visual spatial perception and cognition.

@@

\todo[inline]{SE: mir das Potential (warum ist das relevant -> rich stimulus ie
many possible analyses, better compliance, easier to perform for difficult
populations, etc) eigentlich zu kurz; COH: finde ich (insb. als allerletzten)
Satz in einem Satz so okay, weil a) Textlimit, b) exploratory \& <80 \%
lokalisationsleistung; wenn, dann müsste man ein größeres Fass in Intro und
Discussion aufmachen, was die Ergebnisse aber nicht hergeben }

@@

\todo[inline]{everything correct? Grant or contribution numbers may be acknowledged}
%
COH designed and performed the analyses, and wrote the manuscript.
%
MH provided critical feedback on the procedure and edited the manuscript.
%
SE provided critical feedback.
%
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
annotation of nouns and created its preliminary version.%

>>>>

\noindent Generally
\begin{itemize}
    \item https://gin.g-node.org/; upload; datacite.yml; readme; reserve \&
        cite DOI in data availability section
\end{itemize}

@@

%#1 previous studies
Several studies have reported increased hemodynamic activity in the PPA
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep{epstein1998ppa, epstein1999parahippocampal}.
% auditory semantics unclear
However, reports regarding the correlates of processing spatial information in
verbal stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing of spatial information, we
employed naturalistic stimuli, a movie and its audio-description, that were
designed for entertainment.

@@

%#11 question
The fact that clusters of responses to the auditory stimulus are spatially restricted to
the anterior part of clusters from both visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual stimuli compared to a purely auditory stimulus.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence
that the PPA can be divided into functionally subregions that might process
different stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, lescroart2019human, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
In contrast, the aPPA responds more to high-level features of scenes (e.g.
real-word size \citep{park2015parametric}; a scene's abstract category
\citep{marchette2015outside, watson2016patterns}) and objects (e.g. spatial
contextual associations \citep{aminoff2007parahippocampal, aminoff2013role})
than the pPPA.
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA exhibits more coactivation with the occipital visual cortex than the
aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus
% (TOS) anterior
Activity in the aPPA, on the other hand, is found to be correlated with
components of the default mode network, including caudal inferior parietal lobe,
retrosplenial complex, medial prefrontal cortex, and lateral surface of
the anterior temporal lobe \citep{baldassano2013differential,
baldassano2016two}.
% conclusion: subregions
\citet{baldassano2013differential} proposes that the PPA creates a complete
scene representation, based on different aspects of a visual scene processed in
subregions of the PPA.
% Their distinct connectivity properties do suggest that each may be involved
% in specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual
% features like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2007parahippocampal}) as
immanent in both visual and verbal stimuli.

@@

% shortcomings
%#2
Our approach to movie stimulus annotation and event selection differs from previous
reports in the literature.
% PPA: intro
In an earlier study, \citet{bartels2004mapping} manually annotated the content of
movie frames (color, faces, language, and human bodies) and found that the
functional specialization of brain areas is preserved during movie watching.
%
In contrast, we aimed to exploit a cinematographic confound in the structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% results
The group results of the movie stimulus' primary contrast yielded a large
cluster that spans the group overlap of individual PPA ROIs from anterior to
posterior.
% confound of higher perception
The cluster extends into more posterior, earlier visual areas could be an
indication that the temporal averaging across events suffered from insufficient
controlling for confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames (e.g.,
using the open-source solution ``Pliers''\citep{mcnamara2017developing} for feature extraction from a visual
naturalistic stimulus).

@@

%#12 RSC + LOC
Apart from the PPA, results show significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the movie stimulus, more medial
in the audio-description stimulus) for both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly exhibited increased hemodynamic
activity in studies investigating visual spatial perception or navigation (see reviews
\citep{chrastil2018heterogeneity, bettencourt2013role, epstein2019scene})
% not random shit
Thus, our model-driven approach to operationalize spatial perception based on
stimulus annotations reveals focussed activation patterns in networks that are
implicated in visual spatial perception and cognition.

@@

@@

COH designed and performed the analyses, and wrote the manuscript.
%
MH provided critical feedback on the procedure and edited the manuscript.
%
SE provided critical feedback.
%
We are grateful to \href{www.florianschurz.de}{Florian Schurz} who initiated the
annotation of nouns and created its preliminary version.%
